A pipeline to analyse time-course gene expression data

### 2019-11-13 scripts/manuscript.Rmd
Small fix related to previous commit

```{r fig.height=6, fig.width=6}
# order them by their score
cluster2Score = cluster2Score[order(scores_and_labels$scores[genes_in_cluster2, cluster_of_interest])]
dataToPlot = rbind(
    data[cluster2Score[1:4], ],
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest, ])
plot_splines_data(dataToPlot, moanin_model,
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

>>>>

```{r fig.height=6, fig.width=6}
# order them by their score
cluster2Score = genes_in_cluster2[order(scores_and_labels$scores[genes_in_cluster2, cluster_of_interest])]
dataToPlot = rbind(
    data[cluster2Score[1:4], ],
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest, ])
plot_splines_data(dataToPlot, moanin_model,
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```
